---
title: "R4DS Wrangle Exercise 28"
output: html_document
---
***

### 28.2.1 Exercises
***

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)

```


1. Create one plot on the fuel economy data with customised title, subtitle, caption, x, y, and colour labels.

```{r}

ggplot(mpg, aes(displ, hwy)) +
  geom_point(aes(colour = drv)) +
  geom_smooth(se = FALSE) +
  labs(
    x = "Engine displacement (L)",
    y = "Highway fuel economy (mpg)",
    colour = "Car type",
    title = "Fuel efficiency generally decreases with engine size",
    subtitle = "Front-wheel drive vehicles have the best fuel efficiency",
    caption = "Data from fueleconomy.gov"
  )



```


2. The geom_smooth() is somewhat misleading because the hwy for large engines is skewed upwards due to the inclusion of lightweight sports cars with big engines. Use your modelling tools to fit and display a better model.

Plot 1

```{r}
ggplot(mpg, aes(displ, hwy)) +
  geom_point(aes(colour = class)) +
  geom_smooth(se = FALSE, method = "lm") +
  labs(
    x = "Engine displacement (L)",
    y = "Highway fuel economy (mpg)",
    colour = "Car type",
    title = "Fuel efficiency generally decreases with engine size",
    subtitle = "Two seaters (sports cars) are an exception because of their light weight"
    )

```

Plot 2

```{r, warning = FALSE}

ggplot(mpg, aes(displ, hwy)) +
  geom_point(aes(colour = class)) +
  geom_smooth(se = FALSE) +
  facet_grid(class~.)+
  labs(
    x = "Engine displacement (L)",
    y = "Highway fuel economy (mpg)",
    colour = "Car type",
    title = "Fuel efficiency generally decreases with engine size",
    subtitle = "Two seaters (sports cars) are an exception because of their light weight",
    caption = "Data from fueleconomy.gov"
  ) 


```


3. Take an exploratory graphic that you've created in the last month, and add informative titles to make it easier for others to understand.


```{r}

diamonds %>% 
  ggplot(aes(carat)) +
  geom_freqpoly(binwidth = 0.2) +
  labs(title = "The Distribution of Diamonds by Carat is Skewed to The Right", subtitle = "The larger the diamond, the rarer it is in nature")



```



### 28.3.1 Exercises
***

1. Use geom_text() with infinite positions to place text at the four corners of the plot.

```{r}

# Create tibbles of the text labels
label1 <- tibble(displ = Inf, hwy = Inf, label = "label1")
label2 <- tibble(displ = -Inf, hwy = Inf, label = "label2")
label3 <- tibble(displ = -Inf, hwy = -Inf, label = "label3")
label4 <- tibble(displ = Inf, hwy = -Inf, label = "label4")

# Plot...
mpg %>% 
  ggplot(aes(displ, hwy)) +
  geom_point(aes(color = class)) +
  geom_text(aes(label = label), data = label1, vjust = "top", hjust = "right") +
  geom_text(aes(label = label), data = label2, vjust = "top", hjust = "left") +
  geom_text(aes(label = label), data = label3, vjust = "bottom", hjust = "left") +
  geom_text(aes(label = label), data = label4, vjust = "bottom", hjust = "right")


```


2. Read the documentation for annotate(). How can you use it to add a text label to a plot without having to create a tibble?

?annotate

Example below....

```{r}

mpg %>% 
  ggplot(aes(displ, hwy)) +
  geom_point() +
  annotate("text", x = 5, y = 45, label = "Random Text")

```

3. How do labels with geom_text() interact with faceting? How can you add a label to a single facet? How can you put a different label in each facet? (Hint: think about the underlying data.)

if the variable is not specified, geom_text will add the text labels across all facets


```{r}


labelx <- tibble(displ = Inf, hwy = Inf, label = "Increasing engine size is \nrelated to decreasing fuel economy.")

mpg %>% 
  ggplot(aes(displ, hwy)) +
  geom_point(aes(color = class)) +
  geom_smooth(se = FALSE, method = "lm") +
  facet_grid(class~.) +
  geom_text(aes(label = label), data = labelx, vjust = "top", hjust = "right", size = 3)


```


To add a label to a single facet, we just need to specify the facet variable and filter to the observation in the label's dataframe. (In the example below class (variable) and suv (observation)). Similar concept hold true if we want to put a different label in each facet, we probably want to create multiple labels which specify each classes and use multiple geom_text.

```{r}


labely <- tibble(displ = Inf, hwy = Inf, class = "suv", label = "Big car") #I added the column "class" 

mpg %>% 
  ggplot(aes(displ, hwy)) +
  geom_point(aes(color = class)) +
  geom_smooth(se = FALSE, method = "lm") +
  facet_grid(class~.) +
  geom_text(aes(label = label), data = labely, vjust = "top", hjust = "right", size = 5)

```


4. What arguments to geom_label() control the appearance of the background box?

`label.size`, `label.r`, and `label.padding` arguments control the appearance of the background box.

5. What are the four arguments to arrow()? How do they work? Create a series of plots that demonstrate the most important options.

The four arguments to arrow() are: `angle`, `length`, `ends`, and `type`.

`angle`	- The angle of the arrow head in degrees.
`length` -	A unit specifying the length of the arrow head.
`ends` - One of "last", "first", or "both", indicating which ends of the line to draw arrow heads.
`type` - One of "open" or "closed" indicating whether the arrow head should be a closed triangle.

```{r}


mpg %>% 
  ggplot(aes(displ, hwy)) +
  geom_point() +
  geom_segment(aes(x = 1, y = 45, xend = 10, yend = 7), 
               arrow = arrow(angle = 5, length = unit(0.1, "inches"),
      ends = "last", type = "open"))


```

### 28.4.4 Exercises
***

1. Why doesn't the following code override the default scale?

```{r}

df <- tibble(
  x = rnorm(10000),
  y = rnorm(10000)
)

ggplot(df, aes(x, y)) +
  geom_hex() +
  scale_colour_gradient(low = "white", high = "red") +
  coord_fixed()

```

Because we should be using `scale_fill_gradient` with geom_hex

```{r, error = FALSE}

ggplot(df, aes(x, y)) +
  geom_hex() +
  scale_fill_gradient(low = "white", high = "red") +
  coord_fixed()


```

2. What is the first argument to every scale? How does it compare to labs()?

The first argument to every scale is `...`. It works the same way as labs(). 

3. Change the display of the presidential terms by:

Combining the two variants shown above.
Improving the display of the y axis.
Labelling each term with the name of the president.
Adding informative plot labels.
Placing breaks every 4 years (this is trickier than it seems!).

```{r}

yearbreak <- seq.Date(min(presidential$start), max(presidential$end), by = "4 years") # Reserved for the last step, create a sequence of dates with 4 years break.

presidential %>%
  mutate(id = 33 + row_number()) %>%
  ggplot(aes(start, id, colour = party)) +
  geom_point() +
  geom_segment(aes(xend = end, yend = id)) +
  scale_colour_manual(values = c(Republican = "red", Democratic = "blue")) +
  scale_y_continuous(breaks = seq(33, 45, by = 1)) + #Step 2 - improving the display of y axis by adding 1 break in between of the president terms
  geom_text(aes(label = presidential$name), nudge_y= 0.5, size = 3) + # Labelling each term with the name of the president
  labs(title = "Terms of 11 Presidents From Einsenhower to Obama", x = "Year", y = "POTUS id") + # adding informative plot labels to titles, x & y axis.
  theme(legend.position = "bottom") + #moved the legend to the bottom so that we can have a better view of the chart
  scale_x_date(NULL, breaks = yearbreak, date_labels = "'%y") # Last step, placing breaks every 4 year


```


4. Use override.aes to make the legend on the following plot easier to see.

```{r}

ggplot(diamonds, aes(carat, price)) +
  geom_point(aes(colour = cut), alpha = 1/20)

```


Sure....

```{r}
ggplot(diamonds, aes(carat, price)) +
  geom_point(aes(colour = cut), alpha = 1/20) +
  guides(colour = guide_legend(override.aes = list(alpha = 1)))

```

